% ==============================================================================
% PROJECT: PRIME CHIRP | OBSERVATION PROPOSAL
% TO: The LIGO Scientific Collaboration / Virgo Collaboration / KAGRA
% FROM: KishLattice 16pi Initiative
% DATE: February 6, 2026
% ==============================================================================

\documentclass[11pt, letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{titlesec}
\usepackage{amsmath}
\usepackage{fancyhdr}
\usepackage{xcolor}

% --- HEADER STYLE ---
\pagestyle{fancy}
\fancyhf{}
\lhead{\textbf{Project PRIME CHIRP}}
\rhead{Request for Observation: Geometric Time Signals}
\cfoot{\thepage}

\title{\textbf{Project PRIME CHIRP} \\ \large Proposal for the Utilization of Interferometric Gravitational Wave Detectors \\ as Stratum-0 Geometric Time Receivers}
\author{\textbf{Timothy John Kish} \\ \textit{KishLattice 16pi Initiative} \\ Patent Pending: 63/976,915 (KPCT)}
\date{February 6, 2026}

\begin{document}
\maketitle

\begin{abstract}
The KishLattice 16pi Initiative proposes a calibration and synchronization experiment utilizing the existing sensitivity of the LIGO, Virgo, and KAGRA observatories. 
We posit that the "Quantum Noise" currently filtered out by these detectors contains a coherent, non-local geometric signal---the \textbf{Kish Prime Chirp}. 
This proposal outlines the specific frequency bands (multiples of $16/\pi$) and the Prime Number Harmonic signatures (17, 19, 23) broadcast by the Kish Prime Clock Transceiver (KPCT). We invite the collaboration to analyze their stochastic background data for these specific artificial signatures, which serve as a Universal Stratum-0 Time Reference.
\end{abstract}

\section{Introduction: The Signal in the Noise}
Current gravitational wave astronomy focuses on cataclysmic astrophysical events (Black Hole mergers, Neutron Star collisions). To detect these rare events, observatories filter out "constant" background noise.
\textbf{We propose that this background is not random.}
The \textbf{Kish Prime Clock Transceiver (KPCT)} broadcasts a continuous, low-amplitude geometric stress wave locked to the fundamental stiffness of the vacuum ($16/\pi$). To a standard receiver, this appears as static. However, because it is encoded with a \textbf{Prime Number Sequence}, it is mathematically distinguishable from natural entropy.

\section{The Signal Profile}
We request that the LIGO/Virgo data analysis teams inspect their raw strain data ($h(t)$) for the following specific signatures:

\subsection{1. The Fundamental Carrier}
The carrier wave is locked to the Vacuum Modulus:
\[ f_{carrier} \approx 5.09 \text{ Hz} \quad (\text{Derived from } 16/\pi) \]
This frequency manifests as a persistent, non-decaying "hum" in the low-frequency sensitivity band.

\subsection{2. The Prime Chirp Modulation}
The signal is modulated by a repeating sequence of Prime Harmonics to denote "Artificial Origin" (Time-Sync Data):
\begin{itemize}
    \item \textbf{Harmonic A:} $17 \times (16/\pi)$
    \item \textbf{Harmonic B:} $19 \times (16/\pi)$
    \item \textbf{Harmonic C:} $23 \times (16/\pi)$
\end{itemize}
This creates a distinct "Chord" that never occurs in natural astrophysical processes (which typically follow power laws or orbital decay spirals).

\section{Operational Utility}
This is not merely a theoretical search. If detected, the Kish Prime Chirp serves as a \textbf{Universal Stratum-0 Time Source}.
Because the signal propagates via vacuum geometry (stress) rather than electromagnetic radiation, it is immune to relativistic time dilation ($t' = t$).
LIGO and Virgo can thus be repurposed as the world's most accurate "Wireless Clocks," synchronizing global financial and navigation systems to the absolute frame of the vacuum.

\section{Conclusion}
We are not asking for new hardware. The sensitivity ($10^{-21}$) already exists.
We are asking for a \textbf{Filter Adjustment}.
We invite the collaboration to "Listen for the Primes." The signal is there; you have simply been scrubbing it out as noise.

\vspace{1cm}
\noindent \textbf{Contact:} \\
Timothy John Kish(Independent Researcher)\\
Email: TimothyJohnKish@gmail.com \\
Founder: KishLattice 16pi Initiative LLC \\
\textit{Reference Patent Application: 63/976,915}

\end{document}